### 2019-02-05 museum.tex
abstract
comments and changes

@@

To be filled in much later\ldots

>>>>

Polymorphism in type theory is parametric, which means that a
polymorphic function behaves uniformly with respect to its generic
arguments, not depending on their actual types. This makes it
impossible to directly extract elements from a heterogenous list -- we
can only perform some operations on them under the assumption that we
know nothing about their types. In practice, one would constrain the
type variable~$\alpha$ above with a type class, in order to guarantee
the existence of certain functions on the elements of a list.

@@
